Adopting agile in the large: motivations, success factors and challenges

### 2014-04-24 journal/article.tex
Reasons to change: management problems

@@

        &  \multicolumn{2}{l}{Something must be done in order to remain competitive} \\

@@

        &  \multicolumn{2}{l}{Demand for flexibility or responsiveness} \\
        &  &  Demand for responsiveness to changing business needs  \\
        &  &  Adaptation as projects evolve  \\

@@

The most prominent reason for introducing agile methods was the demand to
deliver software faster and more frequently. A common statement was that it was
necessary to reduce the Time To Market (TTM) [P17, P18, P32, P39, P47]. As
stated in one study: ``The market was moving faster than the development group
was able to deliver'' [P38]. Long cycle time, i.e. time from start of project to
delivery, was seen as a problem in itself in some studies [P25, P36]. Many
studies indicated that the organizations set as one of the transformation goals
to deliver software faster [P2, P8]. Other cases described that development was
generally considered as slow [P36, P46, P49].

@@

% * Timeliness, accuracy
% 
% [P15]
% The number of releases needed to be increased, for accuracy

>>>>

-- We avoid numbers in results, such as frequency of a phenomena, except in the
   meta-analysis section.

@@

        &  \multicolumn{2}{l}{Something must be done in order to remain competitive} \\
        &  &  Change is required to stay in business  \\

@@

        &  \multicolumn{2}{l}{Demand for flexibility or responsiveness} \\
        &  &  Demand to accomodate changes efficiently  \\
        &  &  Better responsiveness to customer requests  \\

@@

The most prominent reason for introducing agile methods was the demand to
deliver software faster and more frequently. A common statement was that it was
necessary to reduce the Time To Market (TTM) [P17, P18, P32, P39, P47]. As
stated in one study: ``The market was moving faster than the development group
was able to deliver'' [P38]. Long cycle time, i.e. time from start of project to
delivery, was seen as a problem in itself [P25, P36]. Some studies indicated
that the organizations set as one of the transformation goals to deliver
software faster [P2, P8]. Other cases described that development was generally
considered as slow [P36, P46, P49].

@@

\subsubsection{Internal issues}

The internal issues relate to how software development is managed in the
organization. In many organizations the project management practice was in a
state of dysfunction, and it needed to be corrected.
Management problems were for instance constantly recurring crisis events [P30],
managers ignoring prioritization of tasks [P38], and reluctance towards focusing
on delivering business value [P49].
Some organizations wanted to improve generic project management practice, such
as risk management [P8], management of offshoring [P38], and improving the
quality of life of team members [P44].

Command and control style management where ``a few people, usually those
farthest from the action, made the decisions without directly involving the
developers doing the actual work'' [P44] was brought up as a problem. For
instance, schedules could be dictated by management, and teams had to comply to
them regardless of the workload [P9].

--> Morale?

--> Pressing team members?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

R: Problems with management of software development
R: Desire to improve management of software development

* Command-and-control, distance from power

[P9]
But, project scope and dates were still dictated by upper management.  If a team
was able to adhere to the project dates, it was commonly met by exhaustive
heroics from the team.

[P9]
The senior director saw solutions to the PDP issues in the possibilities of
Agile too, especially in addressing the command and control brittleness,
fundamental organization issues, and empowerment of individual contributors.

[P44]
Primavera’s project managers typically used a command-and-control philosophy—a
few people, usually those farthest from the action, made the decisions without
directly involving the developers doing the actual work. Furthermore,
relationships between the development team and other departments began to
deteriorate because expectations were seldom met.

[P44]
In particular, we had to improve the company’s perceptions of its own
development team, and the team itself had to reduce its deep-rooted dependency
on the organizational hierarchy and break down functional silos within the
department.

[P39]
Last but not least, they wanted to improve collaboration between the product
management team and developers, and to increase team motivation and commitment.

* Projects simply ``fail''

[P21]
The software development teams under this division experience many issues and
challenges during the software development cycle, the main issues are: Failure
of some projects

% * General dysfunction
% 
% [P6]
% At the time, the most visible symptoms of dysfunction in Yahoo! product
% development were at the project and team layer (centered around issues of
% planning, project management, release management, and team interactions), rather
% than at the technical practices or tools layer.
% 
% % [P30]
% % A crisis process was implemented to address critical issues, enabling teams to
% % stop other work to focus on critical issues. The result was no fewer than three
% % “crisis” events per month, with constant change in project schedules.
% 
% [P38]
% Project managers were not forced to communicate and prioritize across projects.
% It was not clear what, if any, progress to expect on a given project. It was up
% to the developer to prioritize to the best of his/her ability.
% 
% [P38]
% project managers who were focused on a particular project and not on the number
% of products actually being produced for the customers
% 
% [P49]
% Long delivery cycles of a year or more were largely the rule, some ending with
% nothing more to show than documentation. The excuse “they kept changing their
% mind” became an easy shield to protect the executive or manager in charge from
% meaningful sanction, despite delivering nothing of business value. Business case
% projections were rarely (never is a strong word) followed up on to determine if
% the originally projected ROI was achieved.

% * General project management
% 
% [P8]
% Managing project risks through earlier identification of problems and easier 
% mitigation of risks;
% 
% [P8]
% Expanding the sourcing options for projects to allow an increased use of offshore 
% resourced.
% 
% [P44]
% When we decided to improve how we build software and increase the quality of
% life for everyone on the team, we found our answer in agile software
% development.
